Bees need larger brains to thrive in urban environments

### 2023-09-08 Manuscript/Ms.Rmd
updates befor saving repo

\textbf{Jose B. Lanuza$^{1}$} \orcidlink{0000-0002-0287-409X} \textbf{, Miguel Á. Collado$^{1,2}$} \orcidlink{0000-0002-4216-317X} \textbf{, Ferran Sayol$^{3,4}$} \orcidlink{0000-0003-3540-7487} \textbf{, Daniel Sol$^{3}$} \orcidlink{0000-0001-6346-6949} \textbf{and Ignasi Bartomeus$^{1}$} \orcidlink{0000-0001-7893-4389}

Jose B. Lanuza$^{1}$ https://orcid.org/0000-0002-0287-409X, Miguel Á. Collado$^{1,2}$ https://orcid.org/0000-0002-4216-317X, Ferran Sayol$^{3}$ https://orcid.org/0000-0003-3540-7487, Daniel Sol$^{3,4}$ https://orcid.org/0000-0001-6346-6949 and Ignasi Bartomeus$^{1}$ https://orcid.org/0000-0001-7893-4389

@@

$^{2}$Departamento de Ciencias de la Computación e Inteligencia Artificial, Universidad de Sevilla, Seville, Spain

$^{3}$Centre for Ecological Research and Forestry Applications (CREAF), Bellaterra, Catalonia, Spain

$^{4}$CSIC, Spanish National Research Council, CREAF-UAB, Catalonia, Spain

>>>>

\textbf{Jose B. Lanuza$^{1,2}$} \orcidlink{0000-0002-0287-409X} \textbf{, Miguel Á. Collado$^{1,3}$} \orcidlink{0000-0002-4216-317X} \textbf{, Ferran Sayol$^{4}$} \orcidlink{0000-0003-3540-7487} \textbf{, Daniel Sol$^{4,5}$} \orcidlink{0000-0001-6346-6949} \textbf{and Ignasi Bartomeus$^{1}$} \orcidlink{0000-0001-7893-4389}

Jose B. Lanuza$^{1,2}$ https://orcid.org/0000-0002-0287-409X, Miguel Á. Collado$^{1,3}$ https://orcid.org/0000-0002-4216-317X, Ferran Sayol$^{4}$ https://orcid.org/0000-0003-3540-7487, Daniel Sol$^{4,5}$ https://orcid.org/0000-0001-6346-6949 and Ignasi Bartomeus$^{1}$ https://orcid.org/0000-0001-7893-4389

@@

$^{2}$German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig

$^{3}$Departamento de Ciencias de la Computación e Inteligencia Artificial, Universidad de Sevilla, Seville, Spain

$^{4}$Centre for Ecological Research and Forestry Applications (CREAF), Bellaterra, Catalonia, Spain

$^{5}$CSIC, Spanish National Research Council, CREAF-UAB, Catalonia, Spain
